ROV report

### 2020-03-24 analysis/reports/rov.Rmd
weird violin plot

### Rarefaction
```{r rarefaction percentiles overall}

>>>>

```{r ggplot rov v percentile}

rescaled_long <- rov_long %>%
  group_by(rov_index) %>%
  mutate(rescaled_val = scales::rescale(val, c(0, 100))) %>%
  ungroup() %>%
  group_by(rov_index, qbinned_lognparts) %>%
  mutate(high_skew = 100 * mean(skew_percentile >= 95),
         low_simpson =100 *mean(simpson_percentile <= 5)) %>%
  ungroup()

ggplot(rescaled_long, aes(x = qbinned_lognparts, y = rescaled_val)) +
  geom_violin() +
  geom_point(aes(y = high_skew)) +
  geom_point(aes(y = low_simpson), color = 'green') +
  theme_bw() +
  facet_wrap(vars(rov_index), scales = "free_y") +
  geom_hline(yintercept = 5)

ggplot(rescaled_long, aes(x = rescaled_val, y = skew_percentile)) +
  geom_point(alpha = .01) +
  theme_bw() +
  facet_wrap(vars(rov_index), scales = "free_y")

```
### Rarefaction
```{r rarefaction percentiles overall}
